How predictable is extinction?

### 2018-10-19 doc/gsa2018_talk.tex
more desc of ROC
organizing end of talk

% explain ROC
% TYPES of errors
\begin{frame}
  \frametitle{Measuring performance: Reciever Operating Characteristic}

@@

  % want to balance two rates: 
  %   true-positive rate -- predicting extinct when actual is extinct
  %   false-positive rate -- predicting extinct when actual is extant

  % curve describes these metrics at various thresholds

  % AUC is integral of ROC -- 0.5 is random classification, 1 is perfect classification

@@

%% figure out way to present this graphically
%\begin{frame}
%  \frametitle{Comparing our models}
%
%  \begin{tabular}{ r c c c c }
%    Model & LOOIC & SE LOOIC & WAIC & SE WAIC \\ 
%    \hline
%    Past and vary & 12790.39 & \alert<2>{178.83} & 12786.06 & \alert<2>{178.77} \\ 
%    No past but vary & 12818.43 & \alert<2>{178.76} & 12815.40 & \alert<2>{178.71} \\ 
%    Past but no vary & 12850.45 & \alert<2>{179.42} & 12848.12 & \alert<2>{179.38} \\ 
%    No past or vary & 12850.87 & \alert<2>{179.46} & 12848.50 & \alert<2>{179.42} \\ 
%    \hline
%  \end{tabular}
%
%\end{frame}

@@

@@

\begin{frame}
  \frametitle{Conclusions}

@@

\appendix

% move to back
\begin{frame}
  \frametitle{A statistical model for predicting extinction}

  \begin{equation}
    \begin{aligned}
      t_{i} &\sim \text{Bernoulli}(\Theta) \\
      \Theta_{i} &= \text{logit}^{-1} (X_{i} B_{w[i], p[i]} + A_{d[i], p[i]}) \\
      B_{w, p} &\sim MVN(\alpha_{p}, \Sigma_{B}) \\
      \alpha_{p} &\sim MVN(\mu, \Sigma_{\alpha}) \\
    % double check this\dots is A MVN dist?
      A_{w, p} &\sim MVN(\delta_{p}, \Sigma_{A}) \\
      \delta_{p} &\sim \mathrm{N}(0, \sigma_{\delta}) \\
      \mu_{d} &\sim 
      \begin{cases}
        N(0, 10) & \text{if } d = 1 \\
        N(-1, 3) & \text{if } d = 2 \\
        N(0, 3) & \text{if } d > 2 \\
      \end{cases}
      \Sigma_{B} &= diag(\tau_{B}) \Omega_{B} diag(\tau_{B}) \\
      \Sigma_{\alpha} &= diag(\tau_{\alpha}) \Omega_{\alpha} diag(\tau_{\alpha}) \\
      \Sigma_{A} &= diag(\tau_{A}) \Omega_{A} diag(\tau_{A}) \\
      \tau_{B} &\sim C^{+}(5) \\
      \tau_{\alpha} &\sim C^{+}(5) \\
      \tau_{A} &\sim C^{+}(5) \\
      \Omega_{B} &\sim LKJ(1) \\
      \Omega_{\alpha} &\sim LKJ(1) \\
      \Omega_{A} &\sim LKJ(1) \\
    \end{aligned}
  \end{equation}

\begin{frame}
  \frametitle{Effects of age on extinction risk, by phylum}

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/hazard_bygroup}

\end{document}

>>>>

  \begin{center}
    \begin{tabular}[c]{ p{2cm} c | p{2cm} | p{2cm} |}
      \cline{3-4} 
      & & \multicolumn{2}{ c |}{Actual class} \\ \cline{3-4}
      & & 1 & 0 \\ \hline
      \multicolumn{1}{| c |}{\multirow{2}{*}{Predicted class}}
      & 1 & TRUE \newline POSITIVE & FALSE \newline POSITIVE \\ \cline{2-4}
      \multicolumn{1}{| c |}{} & 0 & FALSE \newline NEGATIVE & TRUE \newline NEGATIVE \\
      \hline
    \end{tabular}
  \end{center}

@@

@@

@@

\begin{frame}
  \frametitle{Next steps}

  \begin{itemize}
    \item Consider non-linear/threshold effects of covariates (e.g. GAMM, etc.).
    \item What are the possible effects of other, unconsidered covariates (e.g. foram ecology)?
  \end{itemize}

@@

  \begin{itemize}
    \item \alert{The past matters.} Our best supported model includes our historical covariates and allows all effects to vary over time.
    \item 
  \end{itemize}

@@
